% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yu Zi}

\basicInfo{
  (+1) 412-482-0674 $\bullet$
  zyu539@gmail.com $\bullet$
  183 Jeffrey Ter, Sunnyvale, CA 94089
}

\section{Education}
\datedsubsection{\textbf{Carnegie Mellon University }\textit{Master of Information System Management (BIDA)}}{Aug. 2021 -- Aug. 2022}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{\textit{Highest Distinction}} of Faculty of Heinz College
\end{itemize}
\datedsubsection{\textbf{The University of Auckland }\textit{Bachelor of Software Engineering (Honours)}}{Jul. 2014 -- May. 2018}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{\textit{Dean's Honours List}} of Faculty of Engineering (\textit{First Class})
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:} Java, Python, Go, C++, C, JavaScript
  \item \textbf{Other Knowledge:} Cloud Development, PyTorch, Spark, Kubernetes, Databases (e.g., DynamoDB, MySQL)
  \item \textbf{Interests:} Software Engineering, Cloud Computing, Distributed System, Machine Learning
\end{itemize}

\section{Work Experience}
\datedsubsection{\textbf{Amazon.com, Inc., California} \textit{(Software Development Engineer)}}{Oct. 2022 - Now}
\begin{flushleft}
Working in the Follow team under Shopping Experience for customers to follow brands and to receive exclusive benefits, including brand recommendation and bringing exclusive deals
\begin{itemize}
  \item Develop and maintain services that manage all identifiers and metadata of brands across Amazon, serving as the source of truth for brands as followable entites
  \item Build glue jobs and pipelines for data migration between Services while guarantee data quality and service availability.
\end{itemize}
\end{flushleft}

\datedsubsection{\textbf{Kakapo Technologies Limited., New Zealand } \textit{(Software Development Engineer)}}{Apr. 2018 - May. 2021}
\begin{flushleft}
Develop and maintain a website for National Australia Bank to reconcile trade information across disparate systems.\linebreak It regularly extracts data from systems and identifies trades that should be the same, locating any differences
\begin{itemize}
  \item Multiple Python services that run on AWS to monitor the arrival of data from different systems and \linebreak coordinate the graph of thousands of reconciliation actions through \textbf{message queue}
  \item Parsers and Builders that handle the processing and analyzing of data in hundreds of different formats
\end{itemize}
\end{flushleft}
%\datedsubsection{\textbf{SJGTW Electrical Commercial Company, China } \textit{(Intern)}}{Jun. 2017 - Jul. 2017}
%\begin{flushleft}
%Built a tool that automatically classifies building materials given the name and model (with Keras)
%\begin{itemize}
%  \item Used Neural Network to predicate the class of material, achieving a correctness rate of over 80\%
%\end{itemize}
%\end{flushleft}
% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Projects}

\begin{flushleft}
\datedsubsection{\textbf{Generative Model for Survival Analysis}}{\textit{Deep Learning Project} [2022]}
Use Categorical Variational AutoEncoders + Deep Survival Machines (a fully-parametrical network) to build a model for Time-to-Event Survival Analysis. (e.g., when a patient will die)

\datedsubsection{\textbf{Cloud-Based Twitter User Recommendation System}}{\textit{Cloud Computing Project} [2021]}
A cloud-based web service which recommend some close friends of a input user with similar interests to you.
\begin{itemize}
    \item Use Spark to process over 1TB Twitter dataset, clean and pre-calculate interactive \& common hashtag \linebreak \& keyword score between contact users (users who have retweeted or reply to each other)
    \item Processed Dataset stored in MariaDB on Amazon Relational Database Service
    \item A web service respond to user request was deployed on AWS EKS, reaching throughput of 16000 requests/sec,\linebreak within \$1.2/hour budget.
\end{itemize}

\datedsubsection{\textbf{A Naive Raft Consensus for Distributed Systems with Golang}}{\textit{Distributed System Project} [2021]}

\datedsubsection{\textbf{Cloud-based Anomaly Route Detection System}}{\textit{Graduate Research Project} [2017]}
Worked under the supervision of \textit{Dr. Xuyun Zhang} to build a mobile application which can collect real-time trajectory data to analyze if taxi drivers are taking an anomalous route
\begin{itemize}
    \item A cloud-based Java backend to store and normalize route data, train a prediction model periodically, \linebreak and justify the current route with the trained model, achieving a correctness rate of over 90\%
    \item ETL process to deal clean up dataset using Hadoop MapReduce
\end{itemize}
\end{flushleft}

\section{Honors}
\datedline{\textbf{\textit{\nth{11}}} in \textbf{\textit{ACM-ICPC}} Programming Contest \textbf{South Pacific Regional Final}}{2016}
\datedline{\textbf{\textit{\nth{2} Place}}, in \textbf{\textit{New Zealand Programming Contest}} (Tertiary Open Category)}{2016}
\datedline{\textbf{\textit{\nth{87}}} in \textbf{\textit{IEEEXtreme}} Programming (out of 1823 teams, Top 5\%)}{2016}
\datedline{\textbf{\textit{\nth{3} Place}}, in \textbf{\textit{New Zealand Programming Contest}} (Tertiary Intermediate Category)}{2015}

\end{document}
